\Large \bf 6.824 Final Project

### 2014-05-10 writeup/paper.tex
added some more stuff to writeup

Below we describe the different tests. All tests are located at
'mexos/src/<name>/test_test.go' unless otherwise noted.

@@

These charts need to be re-done, numbers were off because of a code bug.
\begin{table}[h]
\begin{tabular}{|l|l|l|l|}
\hline
\multicolumn{4}{|c|}{\cellcolor[HTML]{C0C0C0}{\color[HTML]{000000} \textbf{Vanilla Paxos}}}                              \\ \hline
                              & \textbf{Avg. Client Latency} & \textbf{Avg. Client Thruput} & \textbf{System Thruput} \\ \hline
\multicolumn{4}{|c|}{\textit{PutHash to one key}}                                                                     \\ \hline
\textbf{1 group, 3 replicas}  & 21.6ms/op                    & 46 requests/s                & 85 requests/s           \\ \hline
\textbf{1 group, 10 replicas} & 52.7ms/op                    & 19 requests/s                & 19 requests/s           \\ \hline
\textbf{3 groups, 3 replicas} & 15.4ms/op                    & 65 requests/s                & 70 requests/s           \\ \hline
\multicolumn{4}{|c|}{\textit{PutHash to many keys}}                                                                 \\ \hline
\textbf{1 group, 3 replicas}  & 20.5ms/op                    & 49 requests/s                & 78 requests/s           \\ \hline
\textbf{1 group, 10 replicas} & 74ms/op                      & 14 requests/s                & 19 requests/s           \\ \hline
\textbf{3 groups, 3 replicas} & 21.8ms/op                    & 46 requests/s                & 179 requests/s          \\ \hline
\end{tabular}
\end{table}

%----------------------------------------------------------------------

\begin{table}[h]
\begin{tabular}{|l|l|l|l|}
\hline
\multicolumn{4}{|c|}{\cellcolor[HTML]{C0C0C0}{\color[HTML]{000000} \textbf{Multipaxos}}}                              \\ \hline
                              & \textbf{Avg. Client Latency} & \textbf{Avg. Client Thruput} & \textbf{System Thruput} \\ \hline
\multicolumn{4}{|c|}{\textit{PutHash to one key}}                                                                     \\ \hline
\textbf{1 group, 3 replicas}  & 14.2ms/op                    & 70.4 requests/s              & 88.8 requests/s         \\ \hline
\textbf{1 group, 10 replicas} & 36.9ms/op                    & 27 requests/s                & 31 requests/s           \\ \hline
\textbf{3 groups, 3 replicas} & 14.1ms/op                    & 70.9 requests/s              & 86 requests/s           \\ \hline
\multicolumn{4}{|c|}{\textit{PutHash to many keys}}                                                                   \\ \hline
\textbf{1 group, 3 replicas}  & 13.3ms/op                    & 75.2 requests/s              & 87.4 requests/s         \\ \hline
\textbf{1 group, 10 replicas} & 37.7ms/op                    & 26.5 requests/s              & 31 requests/s           \\ \hline
\textbf{3 groups, 3 replicas} & 15.8ms/op                    & 63.3 requests/s              & 200 requests/s          \\ \hline
\end{tabular}
\end{table}

@@

\subsubsection{Disk Recovery}
For disk recovery, the bottleneck was...

@@

Another bottleneck is network capacity and/or number of messages. As
shown in the latency and thoughput section, the increasing the number
of replicas has an adverse effect on performance since each operation
requires communication with a majority of replicas. Using multipaxos
improves the performance since it decreases the number of RPCs needed
to commit an operation.

\begin{figure}[H]
\centering
\makebox[\textwidth][c]{
\includegraphics[scale=.66]{replicas.png}}
\caption{Performance of a one-group configuration rapidly dteriorates as the number of replicas increases}
\label{fig:replicas}
\end{figure}

\begin{figure}[H]
\centering
\makebox[\textwidth][c]{
\includegraphics[scale=.66]{groups.png}}
\caption{Performance increases linearly as the number of groups increases. There is probably a saturation point, but we didn't have enough cluster machines to reach it.}
\label{fig:groups}
\end{figure}

@@

Another benefit of the paxos optimizations is that with
fewer messages, less disk space is used since less paxos state data
needs to be saved. We also suspect that using UDP would also improve
throughput, as servers that do not recieve a response already
re-transmit their request, making the TCP ack system redundant.

>>>>

Below we describe the different tests. All tests are located at
'mexos/src/$<$name$>$/test\_test.go' unless otherwise noted.

@@

% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass ``xcolor=table'' option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[h]
\begin{tabular}{|l|l|l|l|}
\hline
\multicolumn{4}{|c|}{\cellcolor[HTML]{C0C0C0}{\color[HTML]{000000} \textbf{Vanilla Paxos}}}                           \\ \hline
                              & \textbf{Avg. Client Latency} & \textbf{Avg. Client Thruput} & \textbf{System Thruput} \\ \hline
\multicolumn{4}{|c|}{\textit{PutHash to one key}}                                                                     \\ \hline
\textbf{1 group, 3 replicas}  & 40.3 ms/op                   & 24.8 requests/s              & 27 requests/s           \\ \hline
\textbf{1 group, 10 replicas} & 5370 ms/op                   & 0.18 requests/s              & 2 requests/s            \\ \hline
\textbf{3 groups, 3 replicas} & 62 ms/op                     &                              & 22 requests/s           \\ \hline
\multicolumn{4}{|c|}{\textit{PutHash to many keys}}                                                                   \\ \hline
\textbf{1 group, 3 replicas}  & 40.7 ms/op                   & 24.5 requests/s              & 30 requests/s           \\ \hline
\textbf{1 group, 10 replicas} & 282 ms/op                    & 3.5 requests/s               & 7 requests/s            \\ \hline
\textbf{3 groups, 3 replicas} & 214 ms/op                    & 4.6 requests/s               & 67 requests/s           \\ \hline
\end{tabular}
\end{table}

% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass ``xcolor=table'' option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[h]
\begin{tabular}{|l|l|l|l|}
\hline
\multicolumn{4}{|c|}{\cellcolor[HTML]{C0C0C0}{\color[HTML]{000000} \textbf{Multipaxos}}}                              \\ \hline
                              & \textbf{Avg. Client Latency} & \textbf{Avg. Client Thruput} & \textbf{System Thruput} \\ \hline
\multicolumn{4}{|c|}{\textit{PutHash to one key}}                                                                     \\ \hline
\textbf{1 group, 3 replicas}  & 27 ms/op                     & 37 requests/s                & 47 requests/s           \\ \hline
\textbf{1 group, 10 replicas} & 2360 ms/op                   & 0.42 requests/s              & 3.4 requests/s          \\ \hline
\textbf{3 groups, 3 replicas} & 22 ms/op                     & 45 requests/s                & 45 requests/s           \\ \hline
\multicolumn{4}{|c|}{\textit{PutHash to many keys}}                                                                   \\ \hline
\textbf{1 group, 3 replicas}  & 25 ms/op                     & 40 requests/s                & 45 requests/s           \\ \hline
\textbf{1 group, 10 replicas} & 130 ms/op                    & 7 requests/s                 & 10.3 requests/s         \\ \hline
\textbf{3 groups, 3 replicas} & 40 ms/op                     & 25 requests/s                & 124 requests/s          \\ \hline
\end{tabular}
\end{table}

For a single group case, the difference between three replicas and ten is
striking. The more replicas, the more traffic is needed for a paxos
agreement. Figure 1 demonstrates how throughput suffers as the number
of replicas increases. One other interesting effect is that as the
number of replicas increases, the larger the gap there is between the
single key and multi-key cases. Because there is one group, all puts
touch the same servers. We are unsure what causes this.

Adding more groups increases throughput, however. For evenly
distributed traffic, going from one group to 3 nearly triples the
throughput. Figure 2 shows that this trend continues, so adding groups
linearly improves the throughput of the system. The table shows that
average throughput for a single client may suffer, but this is
probably because the system throughput benchmark creates many clients,
while the client throughput test creates a single client. Having
multiple clients increases the liklihood that a client must wait to
see its request served, since the replicas may be busy serving another
client's request.

\begin{figure}[H]
\centering
\makebox[\textwidth][c]{
\includegraphics[scale=.50]{replicas.png}}
\caption{Performance of a one-group configuration rapidly deteriorates as the number of replicas increases}
\label{fig:replicas}
\end{figure}

\begin{figure}[H]
\centering
\makebox[\textwidth][c]{
\includegraphics[scale=.5]{groups.png}}
\caption{Performance increases linearly as the number of groups increases. There is probably a saturation point, but we didn't have enough cluster machines to reach it.}
\label{fig:groups}
\end{figure}

@@

Multipaxos decreases the number of RPCs needed to reach agreement.

% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass ``xcolor=table'' option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[H]
\centering
\makebox[\textwidth][c]{
\begin{tabular}{|l|l|l|}
\hline
\multicolumn{3}{|c|}{\cellcolor[HTML]{C0C0C0}\textbf{Paxos RPC Counts}}                  \\ \hline
                                 & \textbf{Single Proposer} & \textbf{Multiple Proposer} \\ \hline
\textbf{Normal Paxos}            & 30                       & 89            \\ \hline
\textbf{Paxos with Leaders}      & 20                       & 27                         \\ \hline
\textbf{Leaders and Pre-prepare} & 17                       & 20                         \\ \hline
\end{tabular}
}
\end{table}

\subsubsection{Disk Recovery}
Raw time to write 1GB to database, HDD:  21.470750409s

Raw time to write 1GB to database, SSD:  6.1470524260s

Recovery time of a 1GB database using our system: TBD

@@

Another bottleneck is network capacity and/or number of messages. As
shown in the latency and thoughput section, the increasing the number
of replicas has an adverse effect on performance since each operation
requires communication with a majority of replicas.

@@

Using multipaxos reduces the amount of network communication required,
which improves the throughput and latency by about a factor of
two. Multipaxos also reduces the amount of paxos state information,
since prepares are pre-determined. This saves some disk space.  We
also suspect that using UDP would also improve throughput, as servers
that do not recieve a response already re-transmit their request,
making the TCP ack system redundant.
